Bayesian selection of best subsets via hybrid search

### 2020-02-09 Manuscript/computational statistics/major_revision_1/BayesSubset_SC.tex
additional simulation, modeling setting,  Sig2_y <- 1 + 0.5*sqrt(abs(X1[,1])), and Sig <- riwish(p+p,(p-1)*Psi) #​ mean is Psi and variance of Sig is small.

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{Heatmap.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn,natbib]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{url}
%\usepackage[linkcolor=blue,citecolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
\newcommand{\T}{{ \top}} %
\newcommand{\ua}{{\bf a}} %
\newcommand{\ub}{{\bf b}} %
\newcommand{\uI}{{\bf I}} %
\newcommand{\uH}{{\bf H}} %
\newcommand{\uX}{{\bf X}} %
\newcommand{\ux}{{\bf x}} %
\newcommand{\uy}{{\bf y}} %
\newcommand{\ud}{{\bf d}} %
\newcommand{\uv}{{\bf v}} %
\newcommand{\uV}{{\bf V}} %
\newcommand{\uu}{{\bf u}} %
\newcommand{\um}{{\bf m}} %
\newcommand{\0}{{\boldsymbol 0}} %
\newcommand{\1}{{\boldsymbol 1}} %
\newcommand{\ubeta}{{\boldsymbol \beta}} %
\newcommand{\ueta}{{\boldsymbol \eta}} %
\newcommand{\umu}{{\boldsymbol \mu}} %
\newcommand{\bg}{{\boldsymbol \gamma}} %
\newcommand{\uepsilon}{{\boldsymbol \epsilon}} %
\newcommand{\uSigma}{{\boldsymbol \Sigma}} %
\newcommand{\diag}{{\rm diag}} %
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Computational Statistics}
%
\begin{document}

@@

\section{Simulation study}\label{sec:5}
In this section, we investigate the variable selection performance of our best subset selection algorithm on simulated high-dimensional data. For $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
\begin{eqnarray*}
y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},\sigma^2_y\right),
\end{eqnarray*}
where $(x_{i1},\ldots,x_{ip})$ follows $\text{Normal}(\0_p,\uV)$ with $\uV=(v_{ij})_{p\times p}$ and $v_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$, and $\sigma^2_y$ is variance of error item.

We consider four different cases: 
\begin{itemize}
	\item [(i)] $p=200$, $\rho=0.1$, $\sigma^2_y = 1$,
	\item [(ii)] $p=200$, $\rho=0.9$, $\sigma^2_y = 1$,
	\item [(iii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 1$,
	\item [(iv)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 1$,
	\item [(v)] $p=200$, $\rho=0.1$, $\sigma^2_y = 2$,
	\item [(vi)] $p=200$, $\rho=0.9$, $\sigma^2_y = 2$,
	\item [(vii)] $p=1000$, $\rho=0.1$, $\sigma^2_y = 2$,
	\item [(viii)] $p=1000$, $\rho=0.9$, $\sigma^2_y = 2$.
\end{itemize}
We assume that there is no prior information. Hence, to make our prior distributions non-informative, we set $a_\sigma=b_\sigma=1$ and $\tau=(\log p)^2$, which satisfies the sufficient condition for model selection consistency discussed in Theorem \ref{thm:2}. We further assume that the true number of active predictors is unknown. Hence, we employ the proposed method in Section \ref{sec:4} for varying $k$ with $K=\lceil n^{2/3} \rceil =22$. For the hybrid search algorithm given in Algorithm \ref{alg:3}, we set $T=100$, which is a remarkably small number of iterations compared to existing stochastic search algorithms (e.g., \citealt{kirkpatrick1983optimization, george1993variable, hans2007shotgun}), and marginal correlations between the response and each predictor are used to define the initial value of $\hat{\bg}$. For comparison purposes, we also employ four popular penalized likelihood methods: LASSO \citep{tibshirani1996regression}, the elastic net \citep{zou2005regularization}, SCAD \citep{fan2001variable}, and MCP \citep{zhang2010nearly}, where the regularization parameters or tuning parameters are determined by the extended BIC in \eqref{ebic} to achieve a fair comparison with the proposed method. In this simulation study, LASSO and ENET are implemented by R package \texttt{glmnet} and  MCP and SCAD are performed by R package \texttt{ncvreg}. To evaluate the variable selection performance, we calculate false discovery rate, percentage of selecting the exact true model, average size of the selected model, and mean of Hamming distance based on $2,000$ Monte Carlo replications. False discovery rate is defined as $|\hat{\bg}\setminus \bg_*|/|\hat{\bg}|$ and Hamming distance is defined as $|\hat{\bg}\setminus \bg_* |+|\bg_* \setminus  \hat{\bg}|$, where $\bg_*$ denotes the index set of the true model.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{Heatmap.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn,natbib]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{url}
%\usepackage[linkcolor=blue,citecolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
\newcommand{\T}{{ \top}} %
\newcommand{\ua}{{\bf a}} %
\newcommand{\ub}{{\bf b}} %
\newcommand{\uI}{{\bf I}} %
\newcommand{\uH}{{\bf H}} %
\newcommand{\uX}{{\bf X}} %
\newcommand{\ux}{{\bf x}} %
\newcommand{\uy}{{\bf y}} %
\newcommand{\ud}{{\bf d}} %
\newcommand{\uv}{{\bf v}} %
\newcommand{\uV}{{\bf V}} %
\newcommand{\uu}{{\bf u}} %
\newcommand{\um}{{\bf m}} %
\newcommand{\0}{{\boldsymbol 0}} %
\newcommand{\1}{{\boldsymbol 1}} %
\newcommand{\ubeta}{{\boldsymbol \beta}} %
\newcommand{\ueta}{{\boldsymbol \eta}} %
\newcommand{\umu}{{\boldsymbol \mu}} %
\newcommand{\bg}{{\boldsymbol \gamma}} %
\newcommand{\uepsilon}{{\boldsymbol \epsilon}} %
\newcommand{\uSigma}{{\boldsymbol \Sigma}} %
\newcommand{\uPsi}{{\boldsymbol \Psi}}
\newcommand{\diag}{{\rm diag}} %
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Computational Statistics}
%
\begin{document}

@@

\section{Simulation study}\label{sec:5}
In this section, we investigate the variable selection performance of our best subset selection algorithm on simulated high-dimensional data. We consider two cases. In case I, for $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
\begin{eqnarray*}
	y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},1\right),
\end{eqnarray*}
where $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma=(\Sigma_{ij})_{p\times p}$ and $\Sigma_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$. In case II, for $n=100$, we generate the data $\{(y_i,x_{i1},\ldots,x_{ip}):i=1,\ldots,n\}$ from the following linear regression model:
\begin{eqnarray*}
	y_i\overset{ind}{\sim}\text{Normal}\left(\sum_{j=1}^p \beta_j x_{ij},\sigma^2_{y}\right),
\end{eqnarray*}
where $\sigma^2_{y_i} = 1+0.01\sqrt{x_{i1}}$, $(x_{i1},\ldots,x_{ip})^\T \overset{iid}{\sim}\text{Normal}(\0_p,\uSigma)$ with $\uSigma\sim \mathcal{IW}(\uPsi, p+2)$, $\uPsi,=(\psi_{ij})_{p\times p}$ and $\psi_{ij}=\rho^{|i-j|}$, four $\beta_j$'s are randomly selected and then generated from $\text{Uniform}\{-1,-2,1,2\}$ independently, and the remaining $\beta$-coefficients are set equal to $0$.

For both cases, we consider four different scenarios: (i) $p=200$, $\rho=0.1$, (ii) $p=200$, $\rho=0.9$, (iii) $p=1000$, $\rho=0.1$, and (iv) $p=1000$, $\rho=0.9$. We assume that there is no prior information. Hence, to make our prior distributions non-informative, we set $a_\sigma=b_\sigma=1$ and $\tau=(\log p)^2$, which satisfies the sufficient condition for model selection consistency discussed in Theorem \ref{thm:2}. We further assume that the true number of active predictors is unknown. Hence, we employ the proposed method in Section \ref{sec:4} for varying $k$ with $K=\lceil n^{2/3} \rceil =22$. For the hybrid search algorithm given in Algorithm \ref{alg:3}, we set $T=100$, which is a remarkably small number of iterations compared to existing stochastic search algorithms (e.g., \citealt{kirkpatrick1983optimization, george1993variable, hans2007shotgun}), and marginal correlations between the response and each predictor are used to define the initial value of $\hat{\bg}$. For comparison purposes, we also employ four popular penalized likelihood methods: LASSO \citep{tibshirani1996regression}, the elastic net \citep{zou2005regularization}, SCAD \citep{fan2001variable}, and MCP \citep{zhang2010nearly}, where the regularization parameters or tuning parameters are determined by the extended BIC in \eqref{ebic} to achieve a fair comparison with the proposed method. In this simulation study, LASSO and ENET are implemented by R package \texttt{glmnet} and  MCP and SCAD are performed by R package \texttt{ncvreg}. To evaluate the variable selection performance, we calculate false discovery rate, percentage of selecting the exact true model, average size of the selected model, and mean of Hamming distance based on $2,000$ Monte Carlo replications. False discovery rate is defined as $|\hat{\bg}\setminus \bg_*|/|\hat{\bg}|$ and Hamming distance is defined as $|\hat{\bg}\setminus \bg_* |+|\bg_* \setminus  \hat{\bg}|$, where $\bg_*$ denotes the index set of the true model.
